Irt plot extra

### 2022-12-22 manuscript_v2.Rmd
Figure 4 caption changed
Knitted by MS

  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "11"
    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
  - id            : "12"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
  - id            : "*"
    institution   : "Joint first author"

@@

abstract: |
  Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure. Further understanding the behaviours that influence individual photic exposure patterns may provide insight into volitional contributions to the physiological effects of light and guide bevavioral points of intervention.  Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).

@@

  The psychometric properties of the LEBA indicate the usability to measure light exposure-related behaviours. The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples. The LEBA inventory will be available under the open-access CC-BY-NC-ND license.

@@

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].

An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]. These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022]. Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance]. Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light? We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations. In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire [@bossini2006sensibilita] are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality. It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations. To fill this gap, we here present the development process of a novel self-reported inventory - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.

@@

## Data Collection

@@

## Analytic Strategy

@@

## Ethical Approval

@@

## Data Availability

The present article is a fully reproducible open access "R Markdown" document. All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).

@@

## Development of the Initial Inventory

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items. The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.

## Anonymous Online Survey

Table 1 summarises the survey participants' demographic characteristics. Only participants completing the full LEBA inventory were included. Thus, there are no missing values in the item analyses. (XXX??) participants were excluded from the analysis due to not passing at least one of the "attention check" items. For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. Participants indicated filling out the online survey from various geographic locations, including `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones. For a complete list of geographic locations, see **Supplementary Table 2**.

@@

(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than \|.30\|. 'x' denotes a non-significant item-total correlation. (B) The Scree plot suggested six factors. (C) Hull method indicated that five factors were required to balance the model fit and number of parameters. (D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.

@@

## Known Limitations

@@

- The fifth factor: "using light in the morning and during daytime" exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ). Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor. This particular factor captures our behaviour related to usages of light in the morning and daytime. Since, light exposure during morning and daytime influences our alertness and cognition [@lok2018light; @siraji2021effects], we deemed capturing these behaviours is essential for the sake of completeness of our inventory. However, the possibility of improving the reliability should be investigated further by adding more appropriate and relevant items to this factor.

- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
- The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The comprehensibility of the LEBA is also reflected by the Flesch-Kincaid grade level identification method [@flesch1948new] that suggested a minimum age of 8.33 years and an educational grade of four or higher (US grading system). We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.

@@

To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner. Thus, estimating convergent validity with similar subjective scales was impossible. Alternatively, the validity of the LEBA could be evaluated by administering it conjointly with objective field measurements of light exposure (e.g. with portable light loggers, see literature review). By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure. 
Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach. Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.
Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors. As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts. On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA, which should be targeted in prospective studies.

@@

With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors. In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum. Applying the LEBA inventory can provide insights into light exposure-related habits on a population-based level. Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light consumption and timing.

>>>>

  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "11"
    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
  - id            : "12"
    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
  - id            : "*"
    institution   : "Joint first author"

@@

abstract: |
  Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure. Further understanding the behaviours that influence individual photic exposure patterns may provide insight into the volitional contributions to the physiological effects of light and guide bevavioral points of intervention.  Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).

@@

  The psychometric properties of the LEBA indicate the usability to measure light exposure-related behaviours. The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples. The LEBA inventory is  available under the open-access CC-BY-NC-ND license.

  Instrument webpage: https://leba-instrument.org/
  GitHub repository containing this manuscript: https://github.com/leba-instrument/leba-manuscript

@@

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].

With the introduction of artificial electric light, human behaviour has become dissociated from the light-dark cycle given by solar radiation. People can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources cannot be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence personal light exposure behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].

An extensive body of scientific evidence suggests that improper light exposure may be disruptive for health and well-being, giving rise to a series of adverse consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]. These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].

Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance]. Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018], making the self-report assessment of light properties challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors.

These measurement limitations point to a couple of research challenges which we adressed here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light? We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations. In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire [@bossini2006sensibilita] are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality. It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations. To fill this gap, we here present the development process of a novel self-reported inventory - the Light Exposure Behaviour Assessment (LEBA) - for characterizing diverse light exposure-related behaviours.

@@

## Data collection

@@

## Analytic strategy

@@

## Ethical approval

@@

## Data availability

The present article is a fully reproducible open access "R Markdown" document. All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- is available under an open-access licence (Creative Commons CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).

@@

## Development of the initial item pool

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items. The 48 items were examined independently based on their relevance and representativeness of the construct light-exposure related behaviour by each panel member, and modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.

## Measurement of light exposure behaviour in an online sample

Table 1 summarises the survey participants' demographic characteristics. Only participants completing the full LEBA inventory were included. Thus, there are no missing values in the item analyses. For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements. Participants indicated filling out the online survey from various geographic locations, including `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones. For a complete list of geographic locations, see **Supplementary Table 2**.

@@

(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than \|.30\|. 'x' denotes non-significant correlation. (B) The Scree plot suggested six factors. (C) Hull method indicated that five factors were required to balance the model fit and number of parameters. (D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.

@@

## Known limitations

@@

The fifth factor, "using light in the morning and during daytime", exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ). Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor. This particular factor captures our behaviour related to usages of light in the morning and daytime. Since, light exposure during morning and daytime influences our alertness and cognition [@lok2018light; @siraji2021effects], we deemed capturing these behaviours is essential for the sake of completeness of our inventory. However, the possibility of improving the reliability should be investigated further by adding more appropriate and relevant items to this factor.

During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.

The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.

As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The comprehensibility of the LEBA is also reflected by the Flesch-Kincaid grade level identification method [@flesch1948new] that suggested a minimum age of 8.33 years and an educational grade of four or higher (US grading system). We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.

@@

To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner. Thus, estimating convergent validity with similar subjective scales was impossible. Alternatively, the validity of the LEBA could be evaluated by administering it conjointly with objective field measurements of light exposure (e.g. with portable light loggers, see literature review). By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.

Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach. Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.

Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors. As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts. On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA, which should be targeted in prospective studies.

@@

Here, we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors. In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum. Applying the LEBA inventory can provide insights into light exposure-related habits on a population-based level. Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light consumption and timing.
